---
title       : Explore European Railway Incident Data
subtitle    : Visualization of incident data from the European Railway Agency
author      : Geltmar von Buxhoeveden
job         : Research Assistent
framework   : shower       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Explore European Railway Incident Data
### Visualization of incident data from the European Railway Agency

### **Agenda**
#### Motivation
#### Methodology
#### Result
#### Try the [Live shiny app](http://geltmar.shinyapps.io/spielwiese)
<footer class = 'logo'>
<img src = 'assets/img/logo.jpeg'></img>
</footer>

--- .class #id 

### Motivation
* Since 2006 the European Railway Agency ([ERA](http://www.era.europa.eu)) is collecting railway incident data
* The data is used to define Common Safety Targets ([CST](http://www.era.europa.eu/Core-Activities/Safety/Safety-Performance/Pages/Common-Safety-Targets.aspx))
* **But:** The data from the 26 member states (with railways) is very inconsistent
* **So:** To explore the inconsistencies a shiny app was developed for the coursera class [Developing Data Products](https://class.coursera.org/devdataprod-002)

<footer class = 'logo'>
<img src = 'assets/img/logo.jpeg'></img>
</footer>

---

### Methodology
* Development of an R shiny app
* Make countries selectable
* Make incident types selectable
* Allow to set time span for data

<footer class = 'logo'>
<img src = 'assets/img/logo.jpeg'></img>
</footer>

---

### Result
* Output graphics are done with ggplot2 like this
```{r fig.height=6,fig.width=10}
p <- ggplot(data=rail, aes(x=Country,  fill=factor(Occurrence.type))) +
  geom_bar(stat="bin") +
  coord_flip() +
  guides(fill=guide_legend(title="Type")) +
  labs(title="Country breakdown\n") +
  ylab("Number of Incidents") +
  xlab("Country")
```
<footer class = 'logo'>
<img src = 'assets/img/logo.jpeg'></img>
</footer>

---

### Result
```{r echo=FALSE}
print(p)
```


